\documentclass[12pt]{article}

\title{Background Multiplayer Part}
\author{Henry Pap}

\begin{document}
  \maketitle
  \clearpage 
  
  \section*{Background}
  The video gaming industry has gained a vast interest over the 
  years since it first was introduced with the infamous game 
  Cathode-ray tube amusement device in 1947 running on a cathode ray tube
  (CRT) screen. This was the start of a revolution with classics like Atari
  coming and reshaping the idea of games. A lot of things has happened 
  since, we went from single player games to splitscreen where the concept
  of social playing was first introduced. With the rise of the Internet 
  so came the idea of multiplayer games running across the Internet that 
  % add some interesting facts about the economical growth 
  can connect people all over the world. The industry has branched out 
  into so many directions (consoles, computers, mobiles) to reach even 
  more people, connecting them becomes the real issue. 2.3 billion people
  play video games according to Newzoo's annual \textit{Global Games Market Report}
  in 2018 with an estimate of \$137.9 billion worth of revenue \cite{newzoo}. % a word here.. like revenue ?
  Online video gaming is the key fact for the rise of video gaming usage and 
  with it comes many problems, low latency, high player capacity, security
  and other in-game areas such as anti-cheating. \\
  The most important problem of the mentioned is the low latency as games 
  (real time communication RTC games in particular). Games tend to run in a 
  very high past where different actions from the player correlates to direct 
  impact in the game world affecting surrounding environment (other players
  in the case of online gaming). This is the reason why keeping low latency
  is the most critical requirement of the network which correlates to a high 
  bandwidth requirement from the players. % section 2.6 in the main article 
  The network must also ensure that all the players get same updates at 
  approximately the same time thus the updates should be synchronous (one 
  player can not get the information faster then the others since this would
  give her the higher benefit). \\

  \noindent The most common network architecture solution for online games 
  is the Client/Server where a central server 
  

  
  \bibliographystyle{IEEEtran}
  \bibliography{ref.bib}
\end{document}